\subsection*{Problem 1}
Show that there is no linear space with 200 vertices such that $|e| \in \{ 5,7 \}$ for every edge $e \in \mathcal{E}$
\begin{proof}

\end{proof}

\subsection*{Problem 2}
$H$ is an intersecting linear space with $57$ vertices. What can $H$ be?

\begin{solution}

\end{solution}

\subsection*{Problem 3}
Let $H$ be an intersecting hypergraph ($e \cap f \neq \emptyset$) without singelton edges. Prove that the greedy algorithm properly colors the vertices of $H$ with at most 3 colors for \textit{any} ordering of the vertices.

\begin{proof}

\end{proof}

\subsection*{Problem 4}
What is the minimum number of vertices in a 5-chromatic shift graph?

\begin{solution}

\end{solution}

\subsection*{Problem 5}
Assume that the $n$-element subset of a (2n+1)-element ground set are colored with two colors. Prove that there are no two $n$-sets of the same color with empty intersection.

\begin{proof}

\end{proof}

\subsection*{Problem 6}
Prove that if the edges of the complete bipartite graph $K_{3,7}$ are colored with two colors (red, blue) then there is a monochromatic $K_{2,2}$. Is the statement true for all $K_{3,6}$?

\begin{proof}

\end{proof}

\subsection*{Problem 7}
A hypergraph on $n$ vertices has no three edges $e,f,g$ such that $e \subset f \subset g$. Show that a hypergraph has at most $2 \binom{n}{\lfloor n/2 \rfloor}$ edges.

\begin{proof}

\end{proof}

\subsection*{Problem 8}
Let $H=(V,E)$ be an intersecting simple hypergraph with $|V|=n$, $|E| < 2^{n-1}$. Prove that a new edge can be added to $E$ so that the new hypergraph is still an intersecting simple hypergraph.

\begin{proof}

\end{proof}

\subsection*{Problem 9}
$H$ is a $t$-uniform hypergraph with exactly $2^{t-1}$ edges. Prove that $H$ is 2-chromatic.

\begin{proof}

\end{proof}

\subsection*{Problem 10}
The 3-uniform hypergraph $\mathcal{H}(n)$ is defined as follows. The vertex set $C_3^n$, the set of vectors of length $n$ with coordinates $1,2,3$. Three different vectors define an edge if an only if at each coordinate position they either all agree or all different.

\medskip

\noindent \textit{Question 1}: Is it true that $\mathcal{H}(n)$ is a Steiner triple system on $3^n$ vertices?

\begin{proof}

\end{proof}

\medskip

\noindent \textit{Question 2}: Is it true that for every $n$, the chromatic number of $\mathcal{H}(n)$ is less than 2025?

\begin{proof}

\end{proof}